Biden Predicted to Secure a Minimum 10% Lead in Popular Votes Over Trump in the 2024 Election

### 2024-03-11 outputs/paper.qmd
create scripts and modify the paper and readme

---
title: "Biden Predicted to Secure a Minimum 10% Lead in Popular Votes Over Trump in the 2024 Election"
author: 
  - Boxuan Yi
format: 
  pdf:
    documentclass: article
    geometry: margin = 1in
    abstract: "The dominance of only two political parties in the current US political system adds an extra layer of competitiveness and interest to the presidential election. This paper uses multilevel regression with post-stratification to predict the outcome between the two candidates, Biden and Trump. The model, along with the post-stratification, indicates that Biden is poised to secure a substantial lead of at least 10% in popular votes, suggesting a strong likelihood that the US will continue on a democratic pathway."
date: "10 March 2024"
date-format: "D MMMM YYYY"
number-sections: true
thanks: "Code and data in this analysis is available at: https://github.com/Elaineyi1/2024prediction_USPresidentialElection"
toc: true
bibliography: references.bib
---
```{r}
#| include: false
library(dplyr)
library(ggplot2)
library(knitr)
library(statebins)
library(modelsummary)
library(broom)
library(readr)
library(here)
library(kableExtra)
library(arrow)
```
\newpage
# Introduction
The forthcoming 2024 United States presidential election, scheduled for Tuesday, November 5, 2024 [@270towin270toWin2024], will see US citizens electing to determine the nation’s president and vice president, shaping the pathways of the country for the next four years. The current president Joe Biden, a member of the Democratic Party, is running for re-election, and his predecessor, Donald Trump from the Republican Party, is running for re-election for a nonconsecutive term. Throughout campaigns, political parties articulate their stances and future policies on broader issues such as abortion, immigration, safety, and LGBTQ+ rights. The Democratic and Republican parties typically hold distinct yet steadfast viewpoints, attracting a significant number of supporters among US citizens. However, the post-COVID era has brought about significant changes economically, socially, and politically, making it particularly intriguing to see how these shifts will influence the upcoming 60th quadrennial presidential election.

>>>>

---
title: "Biden Predicted to Secure a Minimum 10% Lead in Popular Votes Over Trump in the 2024 Election"
author: 
  - Boxuan Yi
format: 
  pdf:
    documentclass: article
    geometry: margin = 1in
    abstract: "The dominance of only two political parties in the current US political system adds an extra layer of competitiveness and interest to the presidential election. This paper uses multilevel regression with post-stratification to predict the outcome between the two candidates, Biden and Trump. The model, along with the post-stratification, indicates that Biden is poised to secure a substantial lead of at least 10% in popular votes, suggesting a strong likelihood that the US will continue on a democratic pathway."
date: "11 March 2024"
date-format: "D MMMM YYYY"
number-sections: true
thanks: "Code and data in this analysis is available at: https://github.com/Elaineyi1/2024prediction_USPresidentialElection"
toc: true
bibliography: references.bib
---
```{r}
#| include: false
library(dplyr)
library(ggplot2)
library(knitr)
library(statebins)
library(modelsummary)
library(broom)
library(readr)
library(here)
library(kableExtra)
library(arrow)
```
\newpage
# Introduction
The forthcoming 2024 United States presidential election, scheduled for Tuesday, November 5, 2024 [@270towin270toWin2024], will see US citizens electing to determine the nation’s president and vice president, shaping the pathways of the country for the next four years. The current president Joe Biden, a member of the Democratic Party, is running for re-election, and his predecessor, Donald Trump from the Republican Party, is running for re-election for a nonconsecutive term. Throughout campaigns, political parties articulate their stances and future policies on broader issues such as abortion, immigration, safety, and LGBTQ+ rights. The Democratic and Republican parties typically hold distinct yet steadfast viewpoints, attracting a significant number of supporters among US citizens. However, the post-COVID era has brought about significant changes economically, socially, and politically, making it particularly intriguing to see how these shifts will influence the upcoming 60th quadrennial presidential election.
